Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\subsection{Experiment Result}

>>>>

\subsection{Experiment Result}
\begin{table}[!htb]
	\caption{Experiment Result for Alpha of 0.1}
	\label{test-1}
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		\textbf{ID} & \multicolumn{1}{l|}{\textbf{Regression Detected}} & \multicolumn{1}{l|}{\textbf{Critical Path Analysis Correct}} \\ \hline
		IS1 & Yes & Yes \\ \hline
		IS2 & Yes & Yes \\ \hline
		IS3 & Yes & Yes \\ \hline
		IS4 & Yes & Yes \\ \hline
		IS5 & Yes & Yes \\ \hline
		IS6 & Yes & Yes \\ \hline
		IS7 & Yes & Yes \\ \hline
		ES1 & Yes & Yes \\ \hline
		ES2 & Yes & Yes \\ \hline
		ES3 & Yes & Yes \\ \hline
		ES4 & Yes & Yes \\ \hline
	\end{tabular}
\end{table}
